Towards Automated Merging of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-05-10 sattose/paper.tex
Finished the text I guess

Unsurprisingly, most clones span a part of a method. Just 1.6\% of the methods are cloned fully. More than a quarter of the clones spans over several methods, which makes extracting methods won't work in a case where a clone spans over several methods. About 4.5\% of clones include a constructor. About 3.3\% of clones include a global variable defined in a class.

>>>>

Unsurprisingly, most clones span a part of a method. More than a quarter of the clones (for type 1R) span over several methods, which either requires more advanced refactoring techniques or indicates a non-harmful clone.
